Formalizing the Edmonds-Karp Algorithm

### 2016-03-04 paper/root.tex
modified diagram

  \begin{figure}[!h]
  \centering    
  \begin{tikzpicture}[thick,scale=1, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xlabel = Number of vertices in the network,
        ylabel = Execution time in milliseconds,
      xticklabels={$0$, $1000$,$2000$,$3000$,$4000$},
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

>>>>

  \begin{figure}[!h]
  \centering    
  \begin{tikzpicture}[thick,scale=1, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xlabel = Number of vertices in the network,
        ylabel = Execution time in seconds, %in milliseconds, modify the scale for lables
        xtick = data,
        ytick = data,
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$}, %corresponds to the first column in {SML, Sparse}
        yticklabels = {$0.2$, $1.4$, $4.9$, $9.2$, $23.6$}, %corresponds to the second column in {SML, Sparse}
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]
